### 2020-06-30 6_related.tex
Re-itemize lists that had to be compressed for the revision.

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. The largest studies
we know of consider at most 7 and 6 programming systems,
respectively~\cite{LULESH13, Deakin19}, and the latter only considers
on-node programming models. In both cases, the mini-apps under study
require a separate, tuned implementation (in contrast to Task
Bench). Other studies usually lack a comprehensive evaluation, even if
multiple implementations are available:
(a) The PENNANT reference implementation supports
MPI/OpenMP/MPI+OpenMP~\cite{PENNANT}. A follow-up paper presents a
Regent implementation~\cite{Regent15}.
(b) One follow-up paper for the mini-app CoMD describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.
(c) A report on the Mantevo project~\cite{Mantevo09} describes a number of
mini-apps, but only includes self-comparisons based on reference
implementations.
And (d) A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, of which only two can be compared in an
apples-to-apples manner as the last implementation uses structured
rather than unstructured meshes. A follow-up describes another
implementation in Regent~\cite{Regent15} (comparison vs.~reference
only).

>>>>

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. The largest studies
we know of consider at most 7 and 6 programming systems,
respectively~\cite{LULESH13, Deakin19}, and the latter only considers
on-node programming models. In both cases, the mini-apps under study
require a separate, tuned implementation (in contrast to Task
Bench). Other studies usually lack a comprehensive evaluation, even if
multiple implementations are available:

\begin{itemize}
\item The PENNANT reference implementation supports
MPI/OpenMP/MPI+OpenMP~\cite{PENNANT}. A follow-up paper presents a
Regent implementation~\cite{Regent15}.

\item One follow-up paper for the mini-app CoMD describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.

\item A report on the Mantevo project~\cite{Mantevo09} describes a number of
mini-apps, but only includes self-comparisons based on reference
implementations.

\item A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, of which only two can be compared in an
apples-to-apples manner as the last implementation uses structured
rather than unstructured meshes. A follow-up describes another
implementation in Regent~\cite{Regent15} (comparison vs.~reference
only).
\end{itemize}

### 2020-06-30 7_conclusion.tex
Re-itemize lists that had to be compressed for the revision.

\begin{itemize}[leftmargin=*]

\item METG for current distributed programming systems varies by over
  5 orders of magnitude.  Clearly understanding the needed task
  granularity is an important consideration in choosing a programming
  system for a new application.

@@

\item Systems for large scale data analysis require very large tasks
  (tens of seconds) to scale beyond small node counts,
  reflecting the very coarse tasks and lack of need for strong scaling
  performance in current workloads.

\item Task Bench has proven effective in finding performance issues
  and has lead to substantial improvements in several of the systems
  we study.

\end{itemize}

>>>>

\begin{itemize}
\item METG for current distributed programming systems varies by over
  5 orders of magnitude.  Clearly understanding the needed task
  granularity is an important consideration in choosing a programming
  system for a new application.

@@

\item Systems for large scale data analysis require very large tasks
  (tens of seconds) to scale beyond small node counts,
  reflecting the very coarse tasks and lack of need for strong scaling
  in current workloads.

\item Task Bench has proven effective in finding performance issues
  and has lead to substantial improvements in several systems
  we study.
\end{itemize}
